---
title: "Bootstrap Data Sets"
author: "EKU R User Group"
date: "29 October 2019"
output: html_document
---

## Bootstrapping

Bootstrapping is another form of cross-validation. Instead of systematically leaving out one observation, a bootstrap resamples from the existing data with replacement. A key characteristic of a bootstrap sample is that it contains the same number of observations as the original data set.

To take a look at sampling with replacement more closely, consider a simple vector consisting of the integers from 1 to 10.

```{r}
example <- 1:10
```

A bootstrap sample of `example` will contain 10 randomly selected elements of `example` with replacement sampling, meaning any element may be chosen multiple times, and some elements will not be chosen at all.

```{r}
sample(example, 
       size = 10, 
       replace = TRUE)
```

When sampling from a data frame, we can sample from the unique rows

```{r}
Example <- data.frame(id = seq_len(10), 
                      some_data = rnorm(10))

sample(seq_len(nrow(Example)), 
       size = nrow(Example),
       replace = TRUE)
```

## Challenge

Using samples of size 10, 25, 50, 75, 100, 250, 500, and 1000, create a visualization that shows what percentage of a data set is sampled at each sample size.  Use 100 bootstrap samples per sample size.

## Some helpful hints

Since this challenge is focused on performing the repetitions, we'll give you an easy to use function to get the percentage of a data set used within a bootstrap sample.

```{r}
# n = sample size
percentage_used_bootstrap <- function(n){
  ToyData <- data.frame(id = seq_len(n), 
                        random_data = rnorm(n))
  sampled_id <- sample(seq_len(nrow(ToyData)), 
                       size = n, 
                       replace = TRUE)
  length(unique(sampled_id)) / nrow(ToyData)
}
```

Another hint is that R includes a call that will repeat an expression as many times as you want it to.  See the help file for the `?replicate` function. An example of it's usage is:

```{r}
replicate(n = 3, 
          {
            rnorm(10)
          })
```

Notice that the result is a matrix where each column is a set of 10 randomly generated values. A feature of interest is that if your expression returns a single value, the result will be a vector, instead of a matrix.

```{r}
replicate(n = 3, 
          {
            rnorm(1)
          })
```

