---
title: "Counting with Letters"
author: "EKU R User Group"
date: "28 January 2020"
output: html_document
---

## Mimicking Excel Column Names

You have received a data set for analysis.  The data file has over 150 variables. The first row of the file has descriptive titles for each of the variables.  These titles look something like "Enrollment: What is/was your enrollment status while in your graduate program?"  Even worse, the data dictionary you received defines coding of the likert scales with language such as "Column AB: 1 = Mostly False, 2 = Somewhat False..."

The researcher is not interested in taking the time to assign unique and meaningful variable names to more than 150 variables, and then redoing their codebook to match the new variable names. For the purpose of this project, it is decided that it would be more efficient to assign variable names to the data based on the column position.

The objective of this mini challenge is to translate numeric column position into Excel style column titles.  For instance

* 1 = A
* 2 = B
* 26 = Z
* 27 = AA
* 28 = AB
* 500 = SF

## Some Guidelines

* We will limit ourselves to the range of 1 to 500<sup>1</sup>.  
* Two uncommon operators will be useful for this challenge:
    + `%/%` is the operator for _integer division_. It returns the integer (with no remainder) after division.  For example `13 %/% 5 = 2`, because 5 goes into 13 two times.
    + `%%` is the operator for _remainder division_ (or modulo division). It returns the remainder following division. For example, `13 %% 5 = 3`, because the remainder of `13 / 5` is 3.
* This challenge is very similar to translate base 10 numbers into base 26.  The one caveat is that there is no "0" character.

## The Mini Mini Challenge

Before attempting the full challenge, try using only the first five letters to count to 12.  So the final results will be

```{r}
c( "A",  "B",  "C",  "D",  "E", 
  "AA", "AB", "AC", "AD", "AE", 
  "BA", "BE")
```

Start with the following code:

```{r}
x <- 1:12
MyLetters <- LETTERS[1:5]
```

When you believe you have the challenge solved, use `x <- 1:500` and compare with the output at the end of the challenge description.

## Hints

* Since we are limiting ourselves to two alpha-digits, we can focus on identifying the left digit and the right digit separately.
* For the left digit, look at the output for `x %/% 26`. What does this result tell you about the left digit?
* For the right digit, look at the output for `x %% 26`. What does this result tell you about the right digit?
* `R` has a built in constant called `LETTERS` that lists all of the upper case English letters. You can use this to get letters based on an index.  For instance, `LETTERS[19]` returns `r LETTERS[19]`

## Footnotes

1. With two digits, we can count up to ZZ, or 676. Getting to AAA requires recursion, which is well out of the scope of a mini challenge.

## The Not So Mini Challenge

Repeat the Mini Mini Challenge but use the full alphabet and count to 500.  If your Mini Mini Challenge result was successful, you should be able to make a couple of small modifications to your code to solve the larger challenge.

Start with the following code:

```{r}
x <- 1:30
```

When you believe you have the challenge solved, use `x <- 1:500` and compare with the output at the end of the challenge description.



## Desired Output

```{r, eval = FALSE}
c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", 
"M", "N", "O", "P", "Q", "R", "S", "T", "U", "V", "W", "X", "Y", 
"Z", "AA", "AB", "AC", "AD", "AE", "AF", "AG", "AH", "AI", "AJ", 
"AK", "AL", "AM", "AN", "AO", "AP", "AQ", "AR", "AS", "AT", "AU", 
"AV", "AW", "AX", "AY", "AZ", "BA", "BB", "BC", "BD", "BE", "BF", 
"BG", "BH", "BI", "BJ", "BK", "BL", "BM", "BN", "BO", "BP", "BQ", 
"BR", "BS", "BT", "BU", "BV", "BW", "BX", "BY", "BZ", "CA", "CB", 
"CC", "CD", "CE", "CF", "CG", "CH", "CI", "CJ", "CK", "CL", "CM", 
"CN", "CO", "CP", "CQ", "CR", "CS", "CT", "CU", "CV", "CW", "CX", 
"CY", "CZ", "DA", "DB", "DC", "DD", "DE", "DF", "DG", "DH", "DI", 
"DJ", "DK", "DL", "DM", "DN", "DO", "DP", "DQ", "DR", "DS", "DT", 
"DU", "DV", "DW", "DX", "DY", "DZ", "EA", "EB", "EC", "ED", "EE", 
"EF", "EG", "EH", "EI", "EJ", "EK", "EL", "EM", "EN", "EO", "EP", 
"EQ", "ER", "ES", "ET", "EU", "EV", "EW", "EX", "EY", "EZ", "FA", 
"FB", "FC", "FD", "FE", "FF", "FG", "FH", "FI", "FJ", "FK", "FL", 
"FM", "FN", "FO", "FP", "FQ", "FR", "FS", "FT", "FU", "FV", "FW", 
"FX", "FY", "FZ", "GA", "GB", "GC", "GD", "GE", "GF", "GG", "GH", 
"GI", "GJ", "GK", "GL", "GM", "GN", "GO", "GP", "GQ", "GR", "GS", 
"GT", "GU", "GV", "GW", "GX", "GY", "GZ", "HA", "HB", "HC", "HD", 
"HE", "HF", "HG", "HH", "HI", "HJ", "HK", "HL", "HM", "HN", "HO", 
"HP", "HQ", "HR", "HS", "HT", "HU", "HV", "HW", "HX", "HY", "HZ", 
"IA", "IB", "IC", "ID", "IE", "IF", "IG", "IH", "II", "IJ", "IK", 
"IL", "IM", "IN", "IO", "IP", "IQ", "IR", "IS", "IT", "IU", "IV", 
"IW", "IX", "IY", "IZ", "JA", "JB", "JC", "JD", "JE", "JF", "JG", 
"JH", "JI", "JJ", "JK", "JL", "JM", "JN", "JO", "JP", "JQ", "JR", 
"JS", "JT", "JU", "JV", "JW", "JX", "JY", "JZ", "KA", "KB", "KC", 
"KD", "KE", "KF", "KG", "KH", "KI", "KJ", "KK", "KL", "KM", "KN", 
"KO", "KP", "KQ", "KR", "KS", "KT", "KU", "KV", "KW", "KX", "KY", 
"KZ", "LA", "LB", "LC", "LD", "LE", "LF", "LG", "LH", "LI", "LJ", 
"LK", "LL", "LM", "LN", "LO", "LP", "LQ", "LR", "LS", "LT", "LU", 
"LV", "LW", "LX", "LY", "LZ", "MA", "MB", "MC", "MD", "ME", "MF", 
"MG", "MH", "MI", "MJ", "MK", "ML", "MM", "MN", "MO", "MP", "MQ", 
"MR", "MS", "MT", "MU", "MV", "MW", "MX", "MY", "MZ", "NA", "NB", 
"NC", "ND", "NE", "NF", "NG", "NH", "NI", "NJ", "NK", "NL", "NM", 
"NN", "NO", "NP", "NQ", "NR", "NS", "NT", "NU", "NV", "NW", "NX", 
"NY", "NZ", "OA", "OB", "OC", "OD", "OE", "OF", "OG", "OH", "OI", 
"OJ", "OK", "OL", "OM", "ON", "OO", "OP", "OQ", "OR", "OS", "OT", 
"OU", "OV", "OW", "OX", "OY", "OZ", "PA", "PB", "PC", "PD", "PE", 
"PF", "PG", "PH", "PI", "PJ", "PK", "PL", "PM", "PN", "PO", "PP", 
"PQ", "PR", "PS", "PT", "PU", "PV", "PW", "PX", "PY", "PZ", "QA", 
"QB", "QC", "QD", "QE", "QF", "QG", "QH", "QI", "QJ", "QK", "QL", 
"QM", "QN", "QO", "QP", "QQ", "QR", "QS", "QT", "QU", "QV", "QW", 
"QX", "QY", "QZ", "RA", "RB", "RC", "RD", "RE", "RF", "RG", "RH", 
"RI", "RJ", "RK", "RL", "RM", "RN", "RO", "RP", "RQ", "RR", "RS", 
"RT", "RU", "RV", "RW", "RX", "RY", "RZ", "SA", "SB", "SC", "SD", 
"SE", "SF")
```