---
title: "September 2019 - Sara Incera's Solution"
output: html_document
---





Jackknife Estimation: In statistics, the jackknife is a resampling technique especially useful for variance and bias estimation. The jackknife pre-dates other common resampling methods such as the bootstrap. The jackknife estimator of a parameter is found by systematically leaving out each observation from a dataset and calculating the estimate and then finding the average of these calculations. This is also known as Leave One Out Cross Validation (LOOCV).

```{r}
?ChickWeight
summary(ChickWeight)
```
We have unequal variances on the experimental "Diet" groups



We can create a linear model for the entire data set with the code
```{r}
fit <- lm(weight ~ Time, data = ChickWeight)
fit
```
We could add Time|Chick to control for the intra-subject effect



We can get the R2 value with the code
```{r}
summary(fit)$adj.r.squared
```
These chicks sure get bigger over time as 70% of the variance in weight is explained by time



GOAL: Implement a jackknife procedure to produce a graphical display (such as a histogram or boxplot) of the R2 value for the model estimating weight as a function of time.



We need to create a loop that eliminates one row at the time, calculates the R2 value for each of the linear models, and stores each r-squre in a new variable that we can use to create a histogram.
```{r}
x <- 1:578
RSquares <- numeric(length(x))

for (i in seq_along(x)){
  Shorter <- ChickWeight[-i, ]
  fit <- lm(weight ~ Time, data = Shorter)
  RSquares[i] <- summary(fit)$adj.r.squared
}

RSquares
```

```{r}
hist(RSquares)
```

Why is it right skewed? Are some measures outliers and removing them makes the R square larger? Will these "outlier" measures be all from the same chick? 





```{r}
Dataset <- ChickWeight
Dataset$RSquares <- RSquares
```

```{r}
library(ggplot2)
```



Let's visualize what data points have a particular strong influence in the R square.
```{r}
ggplot(Dataset, aes(Time, weight)) + 
  geom_point(aes(colour = RSquares)) + 
  geom_smooth(method="lm", formula=y~x)
```
As expected, removing dots that are farther from the line result in the R Square getting larger (clear dots farther from the line - dark dots closer to the line).





Are the chicks in a specific diet particularly likely to be outliers?
```{r}
ggplot(Dataset, aes(Time, weight)) + 
  geom_point(aes(colour = RSquares)) + 
  geom_smooth(method="lm", formula=y~x) +
  facet_grid(~Diet)
```
There is a chick in Diet 2 which is not gaining enough weight when compared to his/her peers. This chick might not look as such a big outlier in Diet 1, where there are other chicks not gaining much weight. 




If you have questions, suggestions, and/or comments about the analysis, please contact Sara Incera at sara.incera@eku.edu
